---
title: 'Demo 1: Reconstructing the Logistic Map'
author: "Rick Dale and Harish S. Bhat"
date: "5/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This brief code obtains a simulation of the simple but wonderful logistic map. Note that, as a discrete system, we take the derivative (dx) to be the system at the next time step. This was done in Brunton et al. (2016) and we do this here. See the text in Dale and Bhat for a discussion of discretely vs. continuously updated systems. 

```{r message=FALSE,warning=FALSE}

library(sindyr)
set.seed(666)

as = seq(from=2.1,to=3.99,by=.05) # the range of parameters used
xs = c()
x = .01
for (a in as) {
  xs_temp = c()
  for (i in 1:200) { # iterations per control parameter value
    x = a*x*(1-x)
    xs_temp = rbind(xs_temp,data.frame(a=a,x=x))
  }
  xs = rbind(xs,xs_temp)
}  
xs[1:4,]
dx = as.matrix(xs[2:nrow(xs),])
xs = xs[1:(nrow(xs)-1),]

sindy.obj = sindy(xs=xs,dx=dx) # build the SINDy object
sindy.obj$B # the fit

```

For illustration of the system, we display the system values over the control parameter (`a`), along with the set of features used to reconstruct the logistic map with SINDy.

```{r,fig.height=3}

# 
# let's get some plots
#
par(mfrow=c(1,2))
plot(xs[xs$a==2.1,2],type='l',xlab='t (iteration)',ylab='x',main='a = 2.1',ylim=c(0,1),col='maroon',lwd=2) # under values a=2.2
plot(xs[xs$a==3.95,2],type='l',xlab='t (iteration)',ylab='x',main='a = 3.95',ylim=c(0,1),col='navy',lwd=2) # under values a=3.95

#
# let's model the logistic under particular values
#
par(mfrow=c(1,2))
x.now = xs[xs$a==2.1,][1,]
xs_modeled = xs[xs$a==2.1,][1,]
for (i in 1:200) {
  x.now = features(x.now,3) %*% sindy.obj$B
  xs_modeled = rbind(xs_modeled,x.now)
}
plot(xs_modeled[,2],type='l',xlab='t (iteration)',ylab='x',main='a = 2.1',ylim=c(0,1),col='maroon',lwd=2) # under values a=2.2

x.now = xs[xs$a==3.95,][1,]
xs_modeled = xs[xs$a==3.95,][1,]
for (i in 1:200) {
  x.now = features(x.now,3) %*% sindy.obj$B
  xs_modeled = rbind(xs_modeled,x.now)
}
plot(xs_modeled[,2],type='l',xlab='t (iteration)',ylab='x',main='a = 3.95',ylim=c(0,1),col='navy',lwd=2) # under values a=3.95
```

Here are the data for X and the dx derivation for the discrete update.

```{r,fig.height=5}
par(mfrow=c(1,2))
plot(xs[,1],type='l',cex=.5,pch=15,xlab='t (iteration)',ylab='a') # a
plot(xs[,2],type='p',cex=.25,pch=15,xlab='t (iteration)',ylab='x') # x
par(mfrow=c(1,2))
plot(dx[,1],type='l',cex=.5,pch=15,xlab='t (iteration)',ylab='a',cex.lab=2) # dx
plot(dx[,2],type='l',cex=.5,pch=15,xlab='t (iteration)',ylab='dx',cex.lab=2) # dx

```

The features used to reconstruct

```{r,fig.height=6,fig.width=7}
Theta = features(xs,3) # grid of features
par(mfrow=c(3,3),oma = c(2,0,0,0) + 0.1,mar = c(1,1,1,1) + 0.5)
for (i in 2:ncol(Theta)) {
  plot(Theta[,i],xlab='t (iteration)',cex.main=2,main=gsub(':','',colnames(Theta)[i]),type='l',xaxt='n',yaxt='n')
}
```





