---
title: 'Demo 4: The Effect of Noise on Two-Attractor Well Reconstruction'
author: "Rick Dale and Harish S. Bhat"
date: "5/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

From:

> Dale, R. & Bhat, H. S. (in press). Equations of mind: Data science for inferring nonlinear dynamics of socio-cognitive systems. *Cognitive Systems Research*.

Taking the simulation of two-attractor well decision making described in Dale and Bhat, we inject noise and demonstrate that SINDy becomes highly unstable. 

```{r message=FALSE,warning=FALSE,fig.width=4}

library(sindyr)

logistic_sindy = function(trials=100,noise=0,more.complex=F) {
  # for GOF tests, here's a desired fit from the Tuller et al. model (Duran & Dale)
  B.expected = matrix(0,nrow=10,ncol=2)
  B.expected[2,1] = 1 # these coefs are only for the "non complex" model
  B.expected[2,2] = -1
  B.expected[3,2] = 2
  B.expected[10,2] = -1
  
  rmses = c()
  deets = c()
  for (i in 1:trials) { # let it go for 100 trials
    x_trial = c()
    x = 0
    k = runif(1)-.5 # choose a random tilt
    x_sum = 0
    for (j in 1:1000) { # let it take at most 1000 cycles to settle
      x_trial = rbind(x_trial,data.frame(k=k,x=x,x_sum=x_sum,j=j)) # store this trial
      if (more.complex) {
        x = x + (-k + x + x^2 - x^3) + noise*(rnorm(1)) # note the additional term x^2
      } else {
        x = x + (-k + x - x^3) + noise*(rnorm(1)) # add noise, increment by model
      }
      x_sum = x_sum + x
      
      if (abs(x_sum)>20) { 
        break; # did it reach threshold? if so, done and exit
      }
      
    }
    
    deets = rbind(deets,x_trial)
  }
  xs=deets[1:(nrow(deets)-1),1:2]
  dx=as.matrix(deets[2:nrow(deets),1:2])
  non.zeros = dx[,2]!=0&xs[,2]!=0
  sindy.obj = sindy(xs=xs[non.zeros,1:2],dx=dx[non.zeros,1:2],lambda=.6,B.expected=B.expected)
  return(sindy.obj)
}

# let's rerun the simulation here
rmses = c()
set.seed(666) # to reproduce exact figs
for (noise in seq(from=0,to=2,length=50)) { # noise level varies
  sindy.obj = logistic_sindy(noise=noise)
  rmses = rbind(rmses, data.frame(noise=noise,rmse=sindy.obj$B.err))
}
# plot the error by noise level... 
plot(rmses$noise,rmses$rmse,type='b',xlab='Noise',ylab='RMSE')

```

When we increase the number of trials collected, it helps overcome the problem of noise.

```{r message=FALSE,warning=FALSE,fig.width=4}

# let's rerun the simulation here
rmses = c()
for (trials in seq(from=50,to=500,length=20)) { # noise level varies
  set.seed(trials) # to reproduce exact figs
  sindy.obj = logistic_sindy(trials=trials,noise=1.5)
  rmses = rbind(rmses, data.frame(trials=trials,rmse=sindy.obj$B.err))
}
# plot the error by noise level... 
plot(rmses$trials,rmses$rmse,type='b',xlab='Number trials',ylab='RMSE')

```

SINDy can be used as a *relative* estimation of model complexity though, and here, despite noise, it can work quite well. Belowe implement two versions of this attractor-well model. Both contain the same level of noise, but one is more complex -- invoking a second term (x^2) in the update equation. The complexity of recovered equations strongly echoes the underlying complexity of the generating system. This suggests that SINDy may be used for *relative* measures of system complexity, not just absolute interpretations from exact recovery.

```{r,fig.width=4}

complexities = c()
noise = 1.5 # set a high noise level, judging from the above simulation

for (iter in 1:100) {

  set.seed(iter) # seed start the same for each condition
  B = logistic_sindy(noise=noise)$B # get coefficients only for this demo
  complexities = rbind(complexities, data.frame(iter=iter,noise=noise,expected=4,complexity=sum(B!=0))) # store data for this run

  set.seed(iter) # seed start the same for each condition
  B = logistic_sindy(noise=noise,more.complex=T)$B # get coefficients only for this demo  
  complexities = rbind(complexities, data.frame(iter=iter,noise=noise,expected=5,complexity=sum(B!=0))) # store data for this more complex run
  
}

summary(lm(complexity~as.factor(expected),data=complexities))
boxplot(jitter(complexity)~as.factor(expected),data=complexities,ylab='Coefficients (with jitter)',xlab='Expected coefficients')


```





